---
title: "ST2137 Tutorial 8"
author: "Wei Hao Khoong"
date: "6 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Q1

## Inversion Method

Let $U = F(X)$. Then $F(X) = 1- (\frac{\beta }{X })^{\alpha }$, for $X \geq \beta $. Hence $X = \frac{\beta }{(1 - U) ^{1 - \alpha }}$.

```{r}
rpareto = function(n, a, b){
  u = runif(n)
  x = b/((1-u)^(1/a))
  return(x)
}
```

```{r}
rpareto(30,4,2)
```

# Q2

## Part (a) - Generating Samples of Size 1000 From Chi-Square Distributions With 6 & 10 Degrees of Freedom Respectively

```{r}
a = 3
b = 5
n = 10^3
x1 = rchisq(n,a*2)
x2 = rchisq(n,b*2)
```

## Part (b) - Generating Samples of Size 1000 From $Beta(3,5)$ Distribution Using Two Samples Obtained In (a)

```{r}
y = x1/(x1+x2)
```

## Part (c) - Histogram With True Density Superimposed

```{r}
# true density
xpt <- seq(0, 1, 0.02)
ypt <- dbeta(xpt, a, b)

# Plotting Density Function
hist(y, freq = F, breaks = seq(0, 1, 0.05))
lines(xpt, ypt)
```

# Q3(a) - $n=9$

```{r}
realmu=c(-1,-0.5,0.5,1)
power=numeric(length(realmu))
ns=1000

means = numeric(ns)
sds = numeric(ns)
for(mu in realmu){
  for(i in 1:ns){
    X = rnorm(9,mu,2)
    means[i]=mean(X)
    sds[i]=sd(X)
  }
  ts = means/(sds/sqrt(9))
  tcrit = qt(0.975,8)
  power[which(realmu==mu)] = sum(abs(ts) > tcrit)/ns
}

cbind(realmu,power)
```

The power is getting bigger as $\mu$ moves away from the value under $H_0: \mu=0$. 

# Q3(b) - $n=25$

```{r}
for(mu in realmu){
  for(i in 1:ns){
    X = rnorm(25,mu,2)
    means[i]=mean(X)
    sds[i]=sd(X)
  }
  ts = means/(sds/sqrt(25))
  tcrit = qt(0.975,24)
  power[which(realmu==mu)] = sum(abs(ts) > tcrit)/ns
}

cbind(realmu,power)
```

The power is getting bigger with greater magnitude when $n=25$ as compared to $n=9$ as $\mu$ moves away from the value under $H_0: \mu=0$. 

# Q4(a)-(b) - Bootstrap Estimate Of Bias & Standard Error Of 25% Trimmed Mean

```{r}
t10q1 <- read.table("C:/Users/Wei Hao/Desktop/ST2137/Tutorials/Data/price.txt", header=TRUE)
attach(t10q1)
library(boot)
set.seed(123)
tm25 <- function(x,b){
  return(mean(x[b],0.25))
}
boot.tm25 <- boot(price, statistic=tm25, R=10000)
boot.tm25
```

The estimate for the bias is 0.7744433 while the standard error is 17.81654.

# Q4(c) - 95% Basic Bootstrap Confidence Interval Of 25% Trimmed Mean

```{r}
boot.ci(boot.tm25, type=c("basic","norm","perc"))
```

The 95% basic bootstrap confidence interval is $(205.5, 275.3)$ while the confidence interval using the bootstrap percentile method is $(212.7, 282.5)$.

# Q4(d) - 5% Confidence Interval For The 25% Trimmed Mean Using Bootstrap Percentile Method

```{r}
# without boot package
ns=10000 #number of bootstrap samples
tm25.sim = numeric(ns)

for(i in 1:ns) {
  tm25.sim[i]=mean(price[sample(length(price),replace=TRUE)],0.25)
}
est = mean(price,0.25) # original estimate
biashat = mean(tm25.sim) - est
sdhat = sd(tm25.sim)
alpha = 0.05
low = quantile(tm25.sim,alpha/2)
high = quantile(tm25.sim,1-alpha/2)
```

```{r}
biashat
```

```{r}
sdhat
```

```{r}
cat("A",100*(1-alpha),"% bootstrap CI is (",2*est - high,",",2*est-low,")","\n")
```

```{r}
cat("Another",100*(1-alpha),"% bootstrap CI is (",low,",",high,")","\n")
```