---
title: "ST2137 Tutorial 6 Q10"
author: "Wei Hao Khoong"
date: "16 March 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1 (a)

### Data Import

```{r}
t6q1 <- read.table("C:/Users/Wei Hao/Desktop/ST2137/Tutorials/Data/machine.txt", header=TRUE)
attach(t6q1)
```

### Relabelling Columns

```{r}
old <- strength[machine=="O"]
new <- strength[machine=="N"]
```

### QQ Plots

```{r}
qqnorm(old)
```

```{r}
qqnorm(new)
```

### Test If Variances Are Equal

```{r}
var.test(new,old)
```

We need to check the equal variance assumption to decide which t-test to use. According to the F-test, the p-value is $0.4268$ so we conclude that the equal variance assumption holds.

### t-test

```{r}
t.test(new, old, mu=0, alternative="greater", var.equal=TRUE)
```

Since we are testing for $H_0 :\mu_N - \mu_O = 0$ against $H_q: \mu_N - \mu_O > 0$, and that $t_{obs} = 3.93 > t_0.05 (98) = 1.66$ or p-value $=7.905 \times 10^{-5}$, we reject $H_0$.

## Q1(b)

We made the assumption that the variances are equal. As above, we have shown that we did not reject the null hypothesis where the variances are equal. 

To check the normality assumption, we employ the Kolmogorov-Smirnov test and look at the QQ plots as well. The results below show that this is a reasonable assumption.

```{r}
ks.test(old,"pnorm",mean(old),sd(old))
```

```{r}
ks.test(new,"pnorm",mean(new),sd(new))
```

### QQ Plots

```{r}
par(mfrow=c(2,1))
qqnorm(old,main="QQ Plot for Old machine")
qqline(old,lty=2)
qqnorm(new,main="QQ Plot for New machine")
qqline(new,lty=2)
par(mfrow=c(1,1))
```