---
title: "ST2137 Tutorial 6 Q3"
author: "Wei Hao Khoong"
date: "16 March 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q3

### Data Import

```{r}
t6q3 <- read.table("C:/Users/Wei Hao/Desktop/ST2137/Tutorials/Data/weeklies.txt",header=T,sep=",")
attach(t6q3)
```

### Paired t-test

```{r}
t.test(current,lastyear,paired=T)
```

Let $\mu_C$ and $\mu_L$ be the mean number of advertising pages in the current issues and the same issue in the previous year respectively. The data points are paired so we will use a paired t-test. We test 

$$H_0: \mu_C - \mu_L = 0 \text{ against } H_1: \mu_C - \mu_L \neq 0$$

Since the observed $t =1.85$ (or p-value $= 0.0803$), we do not reject $H_0$. We conclude that there is insufficient evidence to show a difference in the mean number of advertising pages in the current issues compared to the previous year. A $95\%$ confidence interval estimate of the mean difference in the number of advertising pages in the current issues compared to the previous year is given by $(-21.42, 1.3398)$.

